Rewind: Automatically Generated\\Digital Memories from Mobile Geolocation Data

### 2016-08-28 paper/uist_2016/paper.tex
more on system

\subsubsection{Hyperlapse Creation} 
The composition of one video recollection is consist of two hundred Google Street View images snapshotting the chosen route. Before stitching the imageries together using StreetviewSequence Javascript Library \cite{streetviewsequence}, we performed pixel-wise adjustment on each Google Street View image to reveal time-specific cues including diurnal cycle, seasonal characteristics and meteorological attributes. To achieve this, we used naive HVS and RGB color space mapping for sky and plantation approximation and modification. Similar to the method described by ****Irfanullah (An efficient approach for sky detection)*****, we generalized color mapping streamlines to estimate sky, cloud and plantation. (need to expand on this and mention Caman) For meteorological conditions in particular, we prepared a NoSQL database populated by data collected from the National Oceanic and Atmospheric Administration (NOAA) weather stations for weather lookup. (need to expand too)
-- to be continued

>>>>

\subsubsection{Hyperlapse Creation} 
Each video recollection created by \textit{Rewind} is composed of two hundred Google Street View image sequences of the chosen route being stitched together using StreetViewSequence \cite{streetviewsequence}. Each incoming Google Street View image has been retrieved with the same dimensions (640 px by 640 px) with similar spatial orientation (FOV, pitch and heading values).

Since environmental characteristics, such as meterorological attributes, of images retrieved using Google Street View Static Image API are not directly exposed nor adjustable, it is hard to conclude if the retrieved images would correctly reflect the timely and ambient properties at the time when the user undertook the path. To compensate for this, we performed pixel-wise adjustment on each Google Street View image to better convey time-specific messages including times of the day, seasonal variances and meterological specifics. Previous work done by \cite{laffont2014transient,shih2013data} have successfully reconstructed images with varying diurnal and seasonal cycles, yet it would be computationally expensive to replicate the proposed techniques on large sets of image data on the browser. Considering each \textit{Rewind} hyperlapse would contain two hundred frames, and lifeloggers would probably not be willing to spare more than one minute waiting for the composition of the video, it would be challenging to incoporate a large training dataset into the rendering pipeline. Due to the stringent timing constraint, we have instead adopted a more generic and naive approach of color space mapping for object segmentation and color adjustment, with the facilitation of CamanJS \cite{caman}.

As the Google Street view images of a given route have been retreived with the same dimensional parameters and optical orientation, locational and spatial information of each image is largely similar (ex. the sky normally resides in the upper 1/3 of the image, but could occupy more than 1/2 of the image at times). We have thus been able to approximate sky and ground regions by generalizing the observed geographical information of the incoming images. We first converted each pixel from RGB represenation into HSV color space. For seasonal changes, we estimated a range of HSV values that could be used for plantation classification, adjusted those HSV values that fell within the range for desired seasonal effects, and converted HSV back to RGB color space for Javascript canvas painting (Figure~\ref{fig:season}). Similarly, for creating nightly effects such as sunset and evening scenes, we adjusted sky colors and applied linear brightness and saturation filters locally and globally (Figure~\ref{fig:timeofday}). As an example of creating the evening scene, we segemented the incoming Google Street View image into three major areas: 1. Approximated sky region 2. Non-sky region in the approximated sky region 3. Approximated Ground region. We then down-scaled the RGB values of each pixel based on the region it is classified in.

For meteorological conditions, we prepared a NoSQL database populated by data collected from the National Oceanic and Atmospheric Administration (NOAA) weather stations for weather lookup (currently only available for images from [anonymized: our state/province]). We adjusted sky colors using a similar technique mentioned previously for overcast, rainy and snowy sky. For determined rainy and snowy periods of time, we overlayed an animated precipitation layer accompanied by corresponding audio effects to emulate the environment partially exposed by the weather data.
